---
title: Publications
bibliography: natverse-papers.bib
csl: elsevier-with-titles.csl
nocite: | 
  @jefferis2007, @cachero2010, @yu2010, @silbering2011, @grosjean2011, @kohl2013, @manton2014, @Costa:2016aa, @Panser:2016aa, @Eichler:2017aa, @Sutcliffe:2017aa, @PrietoGodino:2017aa, @Saumweber:2018aa, @Bogovic376384, @Clemens:2018aa, @Jeanne:2018aa, @Huoviala394403, @Zheng:2018aa, @Chin:2018aa, @Dolan:2018aa, @Ding:2019aa, @Li605634, @Auer546507, @Dolan404277, @Frechter336982, @Sayin259119, @bates2019
---

```{r, eval=FALSE, include=FALSE}
  '`r {bibfile = here::here('content/publications/natverse-papers.bib')
  bb=bibtex::read.bib(bibfile)
  # resort by year
  bb=bb[names(sort(unlist(bb$'year')))]
  paste(paste0('@',names(bb)), collapse = ', ')}`'
```
 

## Citations when using the natverse

If you use the natverse in your work, please cite us. Currently the most appropriate
citations are:

* NBLAST: @Costa:2016aa [10.1016/j.neuron.2016.06.012](https://doi.org/10.1016/j.neuron.2016.06.012)
* Bridging and Mirroring registrations, General natverse: @bates2019 [10.1101/006353](https://doi.org/10.1101/006353)


## Publications using the natverse

<!-- Note that for some reason I needed to use the absolute path + here in the YAML header-->
<!-- although in this snippet, the bare filename without any path worked as expected -->
```{r, include=FALSE}
bb=bibtex::read.bib('natverse-papers.bib')
cat(paste0('@',names(bb)), sep = ', ')
npubs=length(bb)
```


The following `r npubs` publications used the natverse or its direct ancestor 
(the R [AnalysisSuite](https://github.com/jefferis/AnalysisSuite)).
If you use a natverse package in one of your papers, then please let us know. 
You can even add a bibtex formatted record for your publication straight to the
top of our bibliography file
by [following this link](https://github.com/natverse/natverse_hugo/edit/dev_pages/content/publications/natverse-papers.bib). Thanks!

---