---
title: Publications
---

```{r publications-data, include=FALSE}
bib_lines <- readLines("natverse-papers.bib", warn = FALSE, encoding = "UTF-8")
starts <- grep("^[[:space:]]*@[A-Za-z]+[[:space:]]*\\{", bib_lines)
ends <- c(starts[-1] - 1L, length(bib_lines))

extract_field <- function(block, field) {
  pat <- regexpr(sprintf("(?i)\\b%s\\s*=\\s*", field), block, perl = TRUE)
  if (pat[1] == -1) return(NA_character_)
  i <- pat[1] + attr(pat, "match.length")
  n <- nchar(block)
  while (i <= n && substr(block, i, i) %in% c(" ", "\n", "\t")) i <- i + 1L
  if (i > n) return(NA_character_)
  opener <- substr(block, i, i)
  if (opener == "{") {
    depth <- 1L
    j <- i + 1L
    while (j <= n && depth > 0L) {
      ch <- substr(block, j, j)
      if (ch == "{") depth <- depth + 1L
      if (ch == "}") depth <- depth - 1L
      j <- j + 1L
    }
    if (depth != 0L) return(NA_character_)
    return(substr(block, i + 1L, j - 2L))
  }
  if (opener == "\"") {
    j <- i + 1L
    while (j <= n && substr(block, j, j) != "\"") j <- j + 1L
    if (j > n) return(NA_character_)
    return(substr(block, i + 1L, j - 1L))
  }
  j <- i
  while (j <= n && !substr(block, j, j) %in% c(",", "\n")) j <- j + 1L
  trimws(substr(block, i, j - 1L))
}

clean_text <- function(x) {
  if (is.na(x) || !nzchar(x)) return("")
  x <- gsub("[\r\n]+", " ", x)
  x <- gsub("\\\\&", "&", x, fixed = TRUE)
  x <- gsub("[{}]", "", x)
  x <- gsub("\\s+", " ", x)
  trimws(x)
}

first_author_label <- function(author_field) {
  if (is.na(author_field) || !nzchar(author_field)) return("Unknown")
  parts <- strsplit(author_field, "\\s+and\\s+", perl = TRUE)[[1]]
  first <- trimws(parts[1])
  if (grepl(",", first, fixed = TRUE)) {
    surname <- trimws(strsplit(first, ",", fixed = TRUE)[[1]][1])
  } else {
    tokens <- strsplit(first, "\\s+")[[1]]
    surname <- tokens[length(tokens)]
  }
  if (length(parts) > 1) paste0(surname, " et al.") else surname
}

entries <- vector("list", length(starts))
for (i in seq_along(starts)) {
  block <- paste(bib_lines[starts[i]:ends[i]], collapse = "\n")
  key <- sub(
    "^[[:space:]]*@[A-Za-z]+[[:space:]]*\\{[[:space:]]*([^,]+),.*$",
    "\\1",
    bib_lines[starts[i]]
  )
  year <- suppressWarnings(as.integer(clean_text(extract_field(block, "year"))))
  if (is.na(year)) year <- 0L
  title <- clean_text(extract_field(block, "title"))
  journal <- clean_text(extract_field(block, "journal"))
  doi <- clean_text(extract_field(block, "doi"))
  url <- clean_text(extract_field(block, "url"))
  author <- clean_text(extract_field(block, "author"))
  entries[[i]] <- data.frame(
    key = key,
    year = year,
    title = title,
    journal = journal,
    doi = doi,
    url = url,
    author = author,
    stringsAsFactors = FALSE
  )
}

pubs <- do.call(rbind, entries)
pubs <- pubs[!duplicated(pubs$key), ]

# Numbering is chronological: earliest paper = 1.
pubs <- pubs[order(pubs$year, pubs$key), ]
pubs$num <- seq_len(nrow(pubs))

# Display grouped in reverse year order (newest first).
pubs_display <- pubs[order(-pubs$year, -pubs$num), ]
npubs <- nrow(pubs)
```

## Citations when using the natverse

If you use the natverse in your work, please cite us. Currently the most appropriate
citations are:

* General natverse, Bridging and Mirroring registrations: Bates et al. (2020) [10.7554/eLife.53350](https://doi.org/10.7554/eLife.53350) [Citations](https://scholar.google.com/scholar?oi=bibs&hl=en&cites=15956725563295855656,14113925605693818488,6575900754848973462&as_sdt=5)
* NBLAST: Costa et al. (2016) [10.1016/j.neuron.2016.06.012](https://doi.org/10.1016/j.neuron.2016.06.012) [Citations](https://scholar.google.com/scholar?oi=bibs&hl=en&cites=3081482044468278939&as_sdt=5)


## Publications using the natverse

The following `r npubs` publications used the natverse or its direct ancestor
(the R [AnalysisSuite](https://github.com/jefferis/AnalysisSuite)).
If you use a natverse package in one of your papers, then please let us know.
You can even add a bibtex formatted record for your publication straight to the
top of our bibliography file
by [following this link](https://github.com/natverse/natverse_hugo/edit/dev_pages/content/publications/natverse-papers.bib). Thanks!

```{r publications-grouped, results='asis', echo=FALSE}
years <- unique(pubs_display$year)
for (yr in years) {
  cat(sprintf("### %d\n\n", yr))
  cat("<ol>\n")
  rows <- pubs_display[pubs_display$year == yr, ]
  for (i in seq_len(nrow(rows))) {
    r <- rows[i, ]
    author_label <- first_author_label(r$author)
    journal_txt <- if (nzchar(r$journal)) r$journal else "Unknown journal"
    doi_link <- ""
    if (nzchar(r$doi)) {
      doi_link <- sprintf(" <a href=\"https://doi.org/%s\">%s</a>", r$doi, r$doi)
    } else if (nzchar(r$url)) {
      doi_link <- sprintf(" <a href=\"%s\">Link</a>", r$url)
    }
    item <- sprintf(
      "<li value=\"%d\"><strong>%s.</strong> %s, %s (%d).%s</li>",
      r$num, r$title, author_label, journal_txt, r$year, doi_link
    )
    cat(item, "\n")
  }
  cat("</ol>\n\n")
}
```
